\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-03-20 doc/paper.Rmd
my citation problem

```{r sigs-profiles, fig.width = 8, fig.height = 2.5, fig.cap="Bullet land profile (left) and the corresponding signature (right)."}
p1 <- sigs_graphics[[1]] %>% filter(land_id==19) %>%
  ggplot(aes(x = y, y = value)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Profile")

@@

@@

@@

@@

@@

```{r type2, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $wo$. For a window size of $wo = 120$ we see a drop in type II error rate across all type I rates considered. Smaller validation sizes $wv$ are typically associated with a smaller type II error."}
errors %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv))) +
#  facet_grid(.~wo, labeller="label_both") + 
  geom_smooth(aes(group=alpha), se=FALSE, method="loess") +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") +
  scale_shape_discrete("Size of validation\nwindow, wv") +
  xlab(expression("Window size for optimization, "~wo)) +
  ylab("Type II error rate")

>>>>

```{r sigs-profiles, fig.width = 8, fig.height = 2.5, fig.cap="Bullet land profile (left) and the corresponding signature (right) for one of the lands of Hamby-44."}
p1 <- sigs_graphics[[1]] %>% filter(land_id==19) %>%
  ggplot(aes(x = y, y = value)) + geom_line() +
  theme_bw() +
  ylab(expression(paste("Depth (in ",mu,m,")", sep=""))) + 
  xlab(expression(paste("Relative Location (in ",mu,m,")", sep=""))) + 
  ggtitle("Profile")

@@

Lands for all Hamby-44 and Hamby-252 scans are made available through the NIST ballistics database \citep{nist} and were considered, here. Both of these sets of scans are part of the larger Hamby study \citep{hamby} and each consist of twenty known bullets (two each from ten consecutively rifled Ruger P85 barrels) and fifteen questioned bullets (each matching one of the ten barrels). Ground truth for both of these Hamby sets is known and was used to assess correctness of the tests results.

Profiles and signatures were extracted from the Hamby 44 and Hamby 252 data as described in \citet{aoas}.

@@

We used the adjusted Chumbley method as proposed in \citet{hadler} and implemented in the R package `toolmaRk` \citep{toolmark} on all pairwise land-to-land comparisons of the Hamby scans provided by NIST (a total of 85,491 comparisons). The settings for optimizing and validating window sizes, $w_o$ and $w_v$, ranged from $w_o \in [50, 280]$ and $w_v \in \{30, 50\}$, see also figure \ref{fig:type2}.

@@

\hh{For signatures from NIST scans we see three problems: 
\begin{enumerate}
\item type-2 error rate is at best 30\% for a type-1 error rate of 5\%, which is well above the error rates we see for tool marks from screw drivers,
\item the observed type-1 error, which generally close to the nominal type-1 error rate, depends on the size of the optimization window: as the window size increases, the observed type-1 error decreases,
\item the Chumbley-score fails to provide a result for up to 3\% of the cases. This drop-out rate is considerably higher when the two lands are from different sources than when the lands are from the same source. 
\end{enumerate}
}

@@

```{r type2, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 120$ we see a drop in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error."}
errors %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv))) +
#  facet_grid(.~wo, labeller="label_both") + 
  geom_smooth(aes(group=alpha), se=FALSE, method="loess") +
  theme_bw() +
  scale_colour_brewer(expression("Nominal\ntype I error"~alpha), palette="Set2") +
  scale_shape_discrete(expression("Size of\nvalidation\nwindow "~w[v])) +
  xlab(expression("Window size for optimization "~w[o])) +
  ylab("Type II error rate")

@@

### 2018-03-20 doc/paper.tex
my citation problem

\caption{Bullet land profile (left) and the corresponding signature (right).}\label{fig:sigs-profiles}
\end{figure}

@@

@@

@@

\caption{Type II error rates observed across a range of window sizes for optimization $wo$. For a window size of $wo = 120$ we see a drop in type II error rate across all type I rates considered. Smaller validation sizes $wv$ are typically associated with a smaller type II error.}\label{fig:type2}
\end{figure}

>>>>

\caption{Bullet land profile (left) and the corresponding signature (right) for one of the lands of Hamby-44.}\label{fig:sigs-profiles}
\end{figure}

Lands for all Hamby-44 and Hamby-252 scans are made available through
the NIST ballistics database \citep{nist} and were considered, here.
Both of these sets of scans are part of the larger Hamby study
\citep{hamby} and each consist of twenty known bullets (two each from
ten consecutively rifled Ruger P85 barrels) and fifteen questioned
bullets (each matching one of the ten barrels). Ground truth for both of
these Hamby sets is known and was used to assess correctness of the
tests results.

Profiles and signatures were extracted from the Hamby 44 and Hamby 252
data as described in \citet{aoas}.

@@

We used the adjusted Chumbley method as proposed in \citet{hadler} and
implemented in the R package \texttt{toolmaRk} \citep{toolmark} on all
pairwise land-to-land comparisons of the Hamby scans provided by NIST (a
total of 85,491 comparisons). The settings for optimizing and validating
window sizes, \(w_o\) and \(w_v\), ranged from \(w_o \in [50, 280]\) and
\(w_v \in \{30, 50\}\), see also figure \ref{fig:type2}.

@@

\caption{Type II error rates observed across a range of window sizes for optimization $w_o$. For a window size of $w_o = 120$ we see a drop in type II error rate across all type I rates considered. Smaller validation sizes $w_v$ are typically associated with a smaller type II error.}\label{fig:type2}
\end{figure}

@@
